### 2022-02-24 paper/localpsf.tex
updating paper based on advances the last couple months. Work in progress...

Approximation \eqref{eq:translate3} is an improvement upon \eqref{eq:translate1} and \eqref{eq:translate2} that generalizes them both. If \eqref{eq:translate1} holds, then $\mu(x) \approx \mu(x_i)$, and so \eqref{eq:translate3} holds. If \eqref{eq:translate2} holds, then $\mu(x_i)-\mu(x) \approx x_i - x$ because translating a distribution translates its mean, so again \eqref{eq:translate3} holds.

>>>>

Approximation \eqref{eq:translate3} is an improvement upon \eqref{eq:translate1} and \eqref{eq:translate2} that generalizes them both. On one hand, if \eqref{eq:translate1} holds, then $\mu(x) \approx \mu(x_i)$, and so \eqref{eq:translate3} holds. On the other hand, translating a distribution translates its mean, so if \eqref{eq:translate2} holds, then $\mu(x_i)-\mu(x) \approx x_i - x$, so again \eqref{eq:translate3} holds.
